---
title: "Simple experiments with a stateless protocol in ns-3"
output: html_document
---

# Preliminaries

It is assumed that this file is placed in **ns-3.20/** directory. You can compile this file in [RStudio](http://www.rstudio.com) using option **Knit HTML**.

This file sources files from [ns3r git repository](https://github.com/dchaly/ns3r.git).
It is assumed that repository is downloaded under **./../ns3r/** directory.

```{r}
library(ggplot2)
setwd("./../ns3r")
source('trace-parser.R')
source('trace-analysis.R')
setwd("./../ns-3.20")
expfilename = "trickles-p2p"
srcfilename = paste0("scratch/", expfilename, ".cc")
```

This file uses a model which is implemented in file ```r srcfilename``` placed in **ns-3.20/scratch/**. The source code of the file is also available at [Appendix A](# Appendix A. Source code of the experiment) of this document.

# Network model

The ```r srcfilename``` contains a model of the following network:

# Experiments

Test experiment:

```{r}
args <- paste0("--run \"scratch/", expfilename," --bandwidth=1Mbps --delay=200ms --queue=10 --protocol=reno --trace=a.tr\"")
res <- system2("./waf", args, stdout=TRUE)
```

```r args```

```r res```

```{r}
traceExp <- function(expfilename) {
  minbandwidth = 1.0
  maxbandwidth = 3.0
  bandwidthstep = 1.0
  mindelay = 10
  maxdelay = 100
  delaystep = 45
  minqueue = 70
  maxqueue = 100
  queuestep = 5
  protocol = c("reno", "trickles")
  expbw <- c()
  expdel <- c()
  expq <- c()
  expprot <- c()
  expperf <- c()
  expdrops <- c()
  for (bw in seq(minbandwidth, maxbandwidth, by=bandwidthstep)) {
    for (del in seq(mindelay, maxdelay, by=delaystep)) {
      for (q in seq(minqueue, maxqueue, by=queuestep)) {
        for (prot in protocol) {
          tracename <- paste0(prot,".", toString(bw),".",toString(del), ".", toString(q),".tr")
          args <- paste0("--run \"scratch/", expfilename," --bandwidth=", toString(bw),"Mbps --delay=", toString(del),"ms --queue=", toString(q)," --protocol=", prot, " --duration=20 --trace=",tracename,"\"")
          res <- system2("./waf", args, stdout=TRUE)
          expbw <- c(expbw, bw)
          expdel <- c(expdel, del)
          expq <- c(expq, q)
          expprot <- c(expprot, prot)
          if (is.null(attr(res, "status"))) {
            expperf <- c(expperf, as.numeric(unlist(strsplit(res[5], " ", fixed=TRUE))[4]))
          } else {
            expperf <- c(expperf, NA)
          }
        }
      }
    }
  }
  resdf <- data.frame(expbw, expdel, expq, expprot, expperf)
  names(resdf) <- c("bandwidth", "delay", "queue", "protocol", "performance")
  resdf
}

expdata <- traceExp(expfilename)
```

Total of ```r nrow(expdata)``` experiments are made.

# Performance visualisations

```{r}
plotres <- function(expres) {
  mf_labeller <- function(var, value) {
    value <- as.character(value)
    if (var=="delay") {
      value <- paste(value, "ms")
    }
    if (var=="bandwidth") {
      value <- paste(value, "Mb")
    }
    return(value)
  }
  
  tplot <- ggplot(expres, aes(x=queue, y=performance/1000000, group=protocol))+
    geom_point(aes(shape=protocol, colour=protocol), size=2)
  tplot <- tplot + scale_y_continuous(limits=c(0,8),breaks=seq(0,8,1))
  tplot <- tplot + ylab("Performance, MB")+xlab("Queue size, packets")
  tplot <- tplot + facet_grid(delay~bandwidth, labeller=mf_labeller)
  tplot <- tplot+theme_bw()+theme(legend.title=element_blank(), legend.text=element_text(face="bold"),legend.key = element_blank())
  tplot <- tplot+scale_colour_discrete(labels=c("TCP Reno", "Trickles"))+
    scale_shape_discrete(labels=c("TCP Reno", "Trickles"))+
    theme(legend.position="bottom")
  tplot
}

pdf("perfmetrics.pdf")
plotres(expdata)
dev.off()
plotres(expdata)
```

# Appendix A. Source code of the experiment

```{r echo=FALSE}
setwd("scratch/")
cat(readChar(paste0(expfilename,".cc"), 1e4))
setwd("..")
```